Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-12-02 manuscript.Rmd

```{r join_sf}
travel_time_sf <- left_join(x = travel_times_census_join, y = dc_acs_tracts, by = "GEOID") %>%
	st_as_sf() %>%
	st_transform(crs = 102285)
```

>>>>

```{r join_sf}
travel_time_sf <- left_join(x = travel_times_census_join, y = dc_acs_tracts, by = "GEOID") %>%
	st_as_sf() %>%
	st_transform(crs = 102285)

centroids <- cbind(st_coordinates(st_centroid(travel_time_sf)))
```

```{r}
plot(st_geometry(dc_acs_tracts), border="grey")
plot(st_centroid(st_geometry(dc_acs_tracts), of_largest_polygon), add=TRUE, col="blue")
```
